Legacy Data Confounds Genomics Studies

### 2019-08-14 LatexManuscript/MBE/legacy.tex
updated plots and text

\begin{figure}[tbp]
\centering
\includegraphics[width=11cm,keepaspectratio]{PerChromosome.jpg}
\caption{
\textbf{A}
The proportion of $Q$-associated variants per chromosome.
\textbf{B}
Mutation spectrum enrichment of  $Q$-associated variants across each chromosome.
Chromosome 1 has a strong enrichment in *AC${\rightarrow}$*CC mutational pattern.
\textbf{C} The number of $Q$-associated variants per 1Mb window across the genome.
Grey bars indicate regions within and black bars indicate regions outside the 1000 Genomes Project strict mask.
Three regions not flagged by the 1000 Genomes Project strict mask in chromosomes 1, 2 and 17 have more than 30 variants per window.
\textbf{D} Distribution of variant counts per 1Mb window. Where variants that fail the strict mask are in grey and those that pass are in black. 
}  
\label{CountPerChrom}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=10cm,keepaspectratio]{RegionOver10.jpg}
\caption{Manhattan plot of the $-\log_{10}(p)$ values for the reverse GWAS logistic regression analysis for the three 1Mb windows with the most  $Q$-associated variants per 1Mb across the genome.}  
\label{Top10}
\end{figure}

>>>>

\begin{figure}[tbp]
\centering
\includegraphics[width=11cm,keepaspectratio]{PerChromosome.jpg}
\caption{
\textbf{A}
The proportion of $Q$-associated variants per chromosome.
\textbf{B}
Mutation spectrum enrichment of  $Q$-associated variants across each chromosome.
Chromosome 1 has a strong enrichment in *AC${\rightarrow}$*CC mutational pattern.
\textbf{C} The number of $Q$-associated variants per 1Mb window across the genome.
Grey bars indicate regions within and black bars indicate regions outside the 1000 Genomes Project strict mask.
\textbf{D} Blue bars indicate the density of variants passing the strict mask with the *AC${\rightarrow}$*CC mutational pattern whereas red points have the T*T${\rightarrow}$TTT mutational pattern.
Three regions not flagged by the 1000 Genomes Project strict mask in chromosomes 1, 2 and 17 have more than 30 variants per window.
\textbf{E} Distribution of variant counts per 1Mb window. Where variants that fail the strict mask are in grey and those that pass are in black. 
}  
\label{CountPerChrom}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=10cm,keepaspectratio]{RegionOver10.jpg}
\caption{Manhattan plot of the $-\log_{10}(p)$ values for the reverse GWAS logistic regression analysis for the three 1Mb windows with the most  $Q$-associated variants per 1Mb across the genome. 
In these plots, blue points are variants with the *AC${\rightarrow}$*CC mutational pattern whereas red points have the T*T${\rightarrow}$TTT mutational pattern.}  
\label{Top10}
\end{figure}
